R for Clinical Study Reports and Submission

### 2023-07-29 tlf-overview.qmd

Submitting clinical trial results to regulatory agencies is a crucial aspect
of clinical development.
The [Electronic Common Technical Document (eCTD)](https://en.wikipedia.org/wiki/Electronic_common_technical_document)
has emerged as the global standard format for regulatory submissions.
For instance, the United States Food and Drug Administration (US FDA)
[mandates the use of eCTD]((https://www.fda.gov/drugs/electronic-regulatory-submission-and-review/electronic-common-technical-document-ectd))
for new drug applications and biologics license applications.

>>>>

Submitting clinical trial results to regulatory agencies is a crucial aspect
of clinical development.
The [Electronic Common Technical Document (eCTD)](https://en.wikipedia.org/wiki/Electronic_common_technical_document)
has emerged as the global standard format for regulatory submissions.
For instance, the United States Food and Drug Administration (US FDA)
[mandates the use of eCTD](https://www.fda.gov/drugs/electronic-regulatory-submission-and-review/electronic-common-technical-document-ectd)
for new drug applications and biologics license applications.
